% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\usepackage[margin=1.0in]{geometry}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

{\textbf{Getting Started}}

{\textbf{Introduction to NodeJS:}}

Node.js is an open-source, cross-platform, back-end JavaScript runtime
environment that runs on the V8 engine and executes JavaScript code
outside a web browser.

As an asynchronous event-driven JavaScript runtime, Node.js is designed
to build scalable network applications.

\hfill 

{\textbf{ECMAScript (ES6):}}

NodeJS is built against modern versions of V8 which is Google's
open-source high-performance JavaScript and Web Assembly engine, written
in C++. It is used in Chrome and in Node.js, among others. It implements
ECMAScript and Web Assembly, and runs on Windows 7 or later, macOS
10.12+, and Linux systems that use x64, IA-32, ARM, or MIPS processors.
V8 can run standalone, or can be embedded into any C++ application

\hfill

All ECMAScript 2015 (ES6) features are split into three groups for
shipping, staged, and in progress features:

\begin{itemize}
\tightlist
\item
  All shipping features, which V8 considers stable, are turned on by
  default on Node.js and do NOT require any kind of runtime flag.
\end{itemize}

\hfill

\begin{itemize}
\tightlist
\item
  Staged features, which are almost-completed features that are not
  considered stable by the V8 team, require a runtime flag: -\/-harmony.
\end{itemize}

\hfill

\begin{itemize}
\tightlist
\item
  In progress features can be activated individually by their respective
  harmony flag, although this is highly discouraged unless for testing
  purposes. Note: these flags are exposed by V8 and will potentially
  change without any deprecation notice.
\end{itemize}

\hfill    

{\textbf{Why NodeJS:}}

\begin{itemize}
\tightlist
\item
  It is runtime application
\item
  Useful for Server-side application development
\end{itemize}

\hfill    

{\textbf{Why ExpressJS}}\textbf{:}

\begin{itemize}
\tightlist
\item
  It adds server methods to NodeJS
\item
  It supports routing mechanism
\item
  Easily creates APIs
\item
  Middleware Friendly
\end{itemize}

\hfill    
 
\newpage
{\textbf{Development Environment}}



{\textbf{NodeJS}}

The Official Website:{~}

https://nodejs.org/en/



Download:{~}

https://nodejs.org/dist/v14.17.5/node-v14.17.5-x64.msi

\hfill    


{\textbf{Visual Studio Code (IDE)}}

The Official Website:{~}

https://code.visualstudio.com/download

\end{document}
