\documentclass[aspectratio=169,14pt,usenames,dvipsnames]{beamer}
\usetheme{TalentSprint}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{ragged2e}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{tcolorbox}
\usepackage{setspace}
\usepackage{lmodern}
\definecolor{swe}{rgb}{0.19, 0.73, 0.56}
\definecolor{lblue}{RGB}{190,200,198}
\title[Looping Statements - do while]{Looping Statements - do while}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\begin{document}

{\1
\begin{frame} \vspace{35pt}

\subtitle{TalentSprint}
\maketitle
\end{frame}
}


\begin{frame}{Learning Objectives}
At the end of this video you should able to:
\begin{itemize}
\item Understand the need for looping
statements.
\item Understand and use do while loop.
\item Write programs using do while.
\end{itemize}
\end{frame}


\begin{frame}{do...while}
\begin{itemize}
    \item Executes code repeatedly based on boolean
condition.
    \item Executes the body of the loop atleast once.
    \item exit control loop. 
\end{itemize}
\end{frame}



\begin{frame}{Syntax}
\begin{lstlisting}
do  \{ \\
\tab statement;\\
\tab statement;\\
\}while (boolean\_expression);\\
\end{lstlisting}\\

\end{frame}



\begin{frame}{Problem Statement}
Add the natural numbers from 1 until the sum
reaches 100.
\end{frame}

\begin{frame}{Syntax-if}
\begin{lstlisting}
int n = 1;\\
int sum = 0;\\
do \{\\
\tab sum += n;\\
\tab n++;\\
\} while (sum $<$ 100);\\
System.out.println(sum);\\
\end{lstlisting}\\
\end{frame}

\begin{frame}{Problem Statement}
Given any four digit number, print the sum of
numbers, formed by deleting the right most
digit till end
Ex: n = 3456 result is 3838 (3456 + 345 + 34 +
3)
\end{frame}

\begin{frame}{Solution}
\begin{lstlisting}
int sum = 4528;\\
int sum = 0;\\

do \{\\
\tab sum += num;\\
\tab num /= 10\\
\} while (num $>$ 0);\\
System.out.println(sum);\\
\end{lstlisting}
\end{frame}


\begin{frame}{Summary}
\begin{itemize}
    \item do while is an exit control loop.
\item The statements in do while will execute
atleast once.

\end{itemize}
\end{frame}
\end{document}