\documentclass[aspectratio=169,14pt,usenames,dvipsnames]{beamer}
\usetheme{TalentSprint}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{ragged2e}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{tcolorbox}
\usepackage{setspace}
\usepackage{lmodern}
\definecolor{swe}{rgb}{0.19, 0.73, 0.56}
\definecolor{lblue}{RGB}{190,200,198}
\title[Break and Continue Statement]{Break and Continue Statement}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\begin{document}

{\1
\begin{frame} \vspace{35pt}

\subtitle{TalentSprint}
\maketitle
\end{frame}
}


\begin{frame}{Learning Objectives}
At the end of this video you should able to:
\begin{itemize}
\item understand and use break statement.
\item understand and use continue statement.
\end{itemize}
\end{frame}


\begin{frame}{break statement}
\begin{itemize}
    \item Terminate the loop immediately when it is
encountered.
    \item Also used in switch case.
\end{itemize}
\end{frame}



\begin{frame}{Problem Statement}
Add the sum of natural number from 1 until
the sum reaches to 100.
\end{frame}



\begin{frame}{Solution}
\begin{lstlisting}
int n = 1 \\
int sum = 0;\\
while (true)\{\\
\tab sum += n;\\
\tab n++;\\
\tab if (sum $>$ 100) \{\\
\tab \tab break;\\
\tab \}\\
\}\\
System.out.println(sum);
\end{lstlisting}
\end{frame}

\begin{frame}{Control statement}
\begin{itemize}
    \item will not execute the statements specified in
the loop after the continue statement.
    \item passes control to the next iteration of any
looping statements.
\end{itemize}
\end{frame}

\begin{frame}{Problem Statement}
Print sum of all natural numbers between 1 to
100 excluding the numbers which are
multiples of 5.
\end{frame}

\begin{frame}{Solution}
\begin{lstlisting}
int start = 1;\\
int limit = 100;\\
int sum = 0;\\
for (int n=start;n $<$= limit;n++)\{\\
\tab if (num \% 5 == 0) \{\\
\tab \tab continue;\\
\tab \}\\
\tab sum +=n;\\
\}\\
System.out.println(sum);\\
\end{lstlisting}
\end{frame}


\begin{frame}{Summary}
\begin{itemize}
    \item break will terminate the loop.
\item continue will skip the statements specified
with in the loop and passed control to the
next iteration.
\end{itemize}
\end{frame}
\end{document}
