\documentclass[aspectratio=169,14pt,usenames,dvipsnames]{beamer}
\usetheme{TalentSprint}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{ragged2e}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{tcolorbox}
\usepackage{setspace}
\usepackage{lmodern}
\definecolor{swe}{rgb}{0.19, 0.73, 0.56}
\definecolor{lblue}{RGB}{190,200,198}
\title[Looping Statements - while]{Looping Statements - while}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\begin{document}

{\1
\begin{frame} \vspace{35pt}

\subtitle{TalentSprint}
\maketitle
\end{frame}
}


\begin{frame}{Learning Objectives}
At the end of this video you should able to:
\begin{itemize}
\item Understand the need for looping
statements.
\item Understand and use while loop.
\item Write programs using while.
\end{itemize}
\end{frame}


\begin{frame}{Repetition}
The process of repeating a set of instructions
for specific number of times.
\end{frame}

\begin{frame}{Repetition}
The process of repeating a set of instructions
for specific number of times.
\begin{block}{Types of looping statements:}
\begin{itemize}
    \item while
    \item do while
    \item for 
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{While}
\begin{itemize}
    \item Control flow statement.
    \item Executes code repeatedly based on boolean
condition.
    \item Pre-test loop.
\end{itemize}
\end{frame}

\begin{frame}{Syntax}
\begin{lstlisting}
while (boolean\_expression) \{ \\
\tab statement;\\
\tab statement;\\
\}\\
\end{lstlisting}\\
The statement(s) with in the loop will execute
until the boolean expression is false
\end{frame}



\begin{frame}{Problem Statement}
Print first 10 natural numbers.
\end{frame}

\begin{frame}{Syntax-if}
\begin{lstlisting}
int n = 1;\\
while (n $<$= 10) \{\\
\tab System.out.println(n);\\
\tab n++;\\
\}\\
\end{lstlisting}\\
\end{frame}

\begin{frame}{Problem Statement}
Print the sum of even numbers with in the
given range.
\end{frame}

\begin{frame}{Solution}
\begin{lstlisting}
int start = 20;\\
int limit = 40;\\
int sum\_of\_evens = 0;\\
while (start $<$= limit) \{\\
\tab if (start \% 2 == 0) \{\\
\tab \tab sum\_of\_evens += start;\\
\tab  \}\\
\tab start++;\\
\}\\
System.out.println(sum\_of\_evens)\\
\end{lstlisting}
\end{frame}

\begin{frame}{Problem Statement}
Print sum of the digits of a given number.
\end{frame}


\begin{frame}{Solution}
\begin{lstlisting}
int num = 2345;\\
sum = 0;\\
while (num $>$ 0) \{\\
\tab rem = num \% 10;\\
\tab sum += rem;\\
\tab num /=10;\\
\}\\
System.out.println(sum);\\
\end{lstlisting}
\end{frame}



\begin{frame}{Summary}
\begin{itemize}
    \item Three types of looping statements are
while, do while and for.
\item Looping statements are used to execute
block of statement(s) repeatedly for
required number of times.
\item while loop is a pre-test loop..
\end{itemize}
\end{frame}
\end{document}