\documentclass[aspectratio=169,14pt,usenames,dvipsnames]{beamer}
\usetheme{TalentSprint}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{ragged2e}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{tcolorbox}
\usepackage{setspace}
\usepackage{lmodern}
\definecolor{swe}{rgb}{0.19, 0.73, 0.56}
\definecolor{lblue}{RGB}{190,200,198}
\title[Introduction to Strings]{Introduction to Strings}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\begin{document}
{\1
\begin{frame} \vspace{35pt}

\subtitle{TalentSprint}
\maketitle
\end{frame}
}

\begin{frame}{Learning Objectives}
At the end of this video you should able to:
\begin{itemize}
\item learn Defining and print the Strings.
\item learn Defining a sentence and print.
\end{itemize}
\end{frame}

\begin{frame}{What is String?}
\begin{block}{\textcolor{red}{String:}}A sequence of characters.
\end{block}
\end{frame}

\begin{frame}{What is String?}
\begin{block}{\textcolor{red}{String:}}A sequence of characters.
\end{block}
\begin{block}{\textcolor{blue}{Example}}
"Welcome"\\
"Welcome to String concept in Java"\\
"123456"\\
\end{block}
\color{red}String value represents in double quotes(" ")
\end{frame}



\begin{frame}{Creating String}
There are \textcolor{red}{2 Ways}  to represent \textcolor{red}{String} in Java:\\
\begin{block}{Object Type}\\
\textbf{String str1 = new String("Hellow World");}
\end{block}
\begin{block}{Reference Type}\\
\textbf{String str2 = "India";}
\end{block}
\end{frame}

\begin{frame}{Problem Statement}
Define a String variable and print
\end{frame}


\begin{frame}{Solution}
\begin{lstlisting}
Class StringDemo\{\\
\tab public static void main(String args[]) \{\\
\tab String name = new String ("Narendra");\\
\tab System.out.println ("Your Name is :" + name);\\
\tab \}\\
\}\\
\end{lstlisting}
\end{frame}



\begin{frame}{Problem Statement}
Define a sentence and print
\end{frame}


\begin{frame}{Operations on String}
\begin{lstlisting}
public class StringDemo \{\\
\tab public static void main(String args[]) \{\\
\tab \tab String msg = "India is a union of"+ " 29 states and"+ " \\ \tab \tab \tab \tab \tab 7 union territories.";\\
\tab \tab System.out.println (msg);\\
\tab \}\\
\}\\
\end{lstlisting}
\end{frame}




\begin{frame}{Summary}
\begin{itemize}
    \item Learning Defining and print the Strings.
\item Learning Defining a sentence and print.
\end{itemize}
\end{frame}
\end{document}